Figures

### 2021-03-09 inst/manuscript/figures.Rmd
Edited ms and si: first upload to EarthArXiv. Edited scripts for data_for_instances.R, added new script to data-raw (aois_tiles.R) to show creation of degree and tiling grids

### Figure S3: Initial training site distribution
Figure showing distribution of initial 500 samples per cluster, as well as distribution of points per iteration.  
```{r trainingsites, eval=FALSE}
data("train_val_sites")

@@

### Figure S4: Label count and quality
```{r labelquality, eval=FALSE}
data("label_summary")

@@

### Figures S5 and S6: Consensus label (Bayesian) risk

@@

### Figure S7: Random versus active sampling
```{r, eval=FALSE}
data("iteration_metrics")

@@

### Figure S8: Training data error impact on probability images
```{r, eval = FALSE}
probpal <- viridis::viridis
cprob <- raster(here::here("external/prob/image_c294_r532.tif"))
hprob <- raster(here::here("external/prob/image_c294_r532_high.tif"))
lprob <- raster(here::here("external/prob/image_c294_r532_low.tif"))

@@

### Figure S9: AOI Zones

@@

### Figures S10 and S11: Segmentation statistics (grid scale)

@@

### Figure S12: Average fields sizes

@@

Both original as derived from segmentations and adjusted using regression kriging.

```{r, eval=FALSE}
fsizes <- read_stars(
  system.file("extdata/mean_field_size005.tif", package = "activemapper")
)
fsizes_adj <- read_stars(
  system.file("extdata/mean_field_size005_adj.tif", package = "activemapper")
)

# Plots
xylims <- st_bbox(ghana)
p <- ggplot(africa) + 
  geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
  geom_stars(data = fsizes) +
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
  scale_fill_viridis_c(name = "ha", na.value = "transparent") +
  coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) +
  theme_void() + 
  theme(legend.position = c(0.7, 0.07), legend.direction = "horizontal", 
        legend.key.height = unit(0.2, "cm"), 
        legend.text = element_text(colour = "black"),
        legend.title = element_text(size = 9, colour = "black"))

p2 <- ggplot(africa) + 
  geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
  geom_stars(data = fsizes_adj[, , , 1]) +
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
  scale_fill_viridis_c(name = "ha", na.value = "transparent") +
  coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) +
  theme_void() + 
  theme(legend.position = c(0.7, 0.07), legend.direction = "horizontal", 
        legend.key.height = unit(0.2, "cm"), 
        legend.text = element_text(colour = "black"),
        legend.title = element_text(size = 9, colour = "black"))

ggsave(op, bg = "transparent", width = 6, height = 4, units = "in", dpi = 300, 
       filename = pth("figures/si_fsizes.png"))

<!-- ### Figure S10: Segmentation statistics, tile scale -->
<!-- ```{r, eval=FALSE} -->
<!-- data("tile_aoi_validation_stats") -->

<!-- humachine <- tile_aoi_validation_stats$tile %>%  -->
<!--   mutate(type = ifelse(grepl("segments", type), "Segmentation", type), -->
<!--          type = ifelse(grepl("validation", type), "Validation", type)) %>%  -->
<!--   select(type, aoi, tile, area_mu, area_med, n_mu) %>%  -->
<!--   rename(Mean = area_mu, Median = area_med) -->

<!-- humachine_sum <- humachine %>% group_by(aoi, type) %>%  -->
<!--   summarize(Median = median(Mean), Mean = mean(Mean)) %>%  -->
<!--   ungroup() %>%  -->
<!--   tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat") -->

<!-- humachine_sum_n <- humachine %>% group_by(aoi, type) %>%  -->
<!--   summarize(Median = median(n_mu), Mean = mean(n_mu)) %>%  -->
<!--   ungroup() %>%  -->
<!--   tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat") -->

<!-- # Field size -->
<!-- brks <- seq(0, 20, 5) -->
<!-- p <- ggplot(humachine) +  -->
<!--   geom_density(aes(x = Mean, y = ..count.., fill = type), col = "transparent",  -->
<!--                linetype = "blank") +   -->
<!--   geom_vline(data = humachine_sum,  -->
<!--              aes(xintercept = value, color = type, linetype = Stat),  -->
<!--              size = 0.5) + -->
<!--   scale_x_continuous(expand = c(0.03, 0.03), breaks = brks, limits = c(0, 20)) + -->
<!--   scale_y_continuous(expand = c(0, 0)) + -->
<!--   scale_color_manual(name = "", values = c("blue", "red"), guide = FALSE) +  -->
<!--   scale_fill_manual(name = "", values = fcols) +   -->
<!--   # scale_linetype_manual(name = "", values = c("dashed", "solid")) +   -->
<!--   scale_linetype("") +   -->
<!--   facet_wrap(vars(aoi)) +  -->
<!--   xlab("Field size (ha)") + ylab("Count") +  -->
<!--   theme_fun() -->
<!-- ggsave(pth("figures/si_tile_validation_stats_fha.png"),  -->
<!--        width = 7, height = 7, units = "in", dpi = 300) -->

<!-- # field number -->
<!-- brks <- seq(0, 20, 5) -->
<!-- p2 <- ggplot(humachine) +  -->
<!--   geom_density(aes(x = n_mu, y = ..count.., fill = type), col = "transparent",  -->
<!--                linetype = "blank") +   -->
<!--   geom_vline(data = humachine_sum_n,  -->
<!--              aes(xintercept = value, color = type, linetype = Stat),  -->
<!--              size = 0.5) + -->
<!--   scale_x_continuous(expand = c(0.03, 0.03), breaks = brks, limits = c(0, 20)) + -->
<!--   scale_y_continuous(expand = c(0, 0)) + #, limits = c(0, 40)) + -->
<!--   scale_color_manual(name = "", values = c("blue", "red"), guide = FALSE) +  -->
<!--   scale_fill_manual(name = "", values = fcols) +   -->
<!--   # scale_linetype_manual(name = "", values = c("dashed", "solid")) +   -->
<!--   scale_linetype("") +   -->
<!--   facet_wrap(vars(aoi)) +  -->
<!--   xlab("Number of fields") + ylab("Count") +  -->
<!--   theme_fun() -->
<!-- ggsave(pth("figures/si_tile_validation_stats_fn.png"),  -->
<!--        width = 7, height = 7, units = "in", dpi = 300) -->
<!-- ``` -->

<!-- ### Figure S11: Segmentation statistics: grid, tile, and AOI scales -->

<!-- Read back in segments to get distributions -->
<!-- ```{r, eval = FALSE} -->
<!-- data("tile_aoi_validation_stats") -->

<!-- # # Read in segments, drop old AOI3 -->
<!-- # segment_files <- dir(here("external/data/results/segments/merged"), -->
<!-- #                      pattern = "boundarymerge", full.names = TRUE) -->
<!-- # iid <- as.numeric(gsub("[[:alpha:]]|_|\\.", "", basename(segment_files))) -->
<!-- # segment_files <- tibble(file = segment_files, order = iid) %>% arrange(iid) -->
<!-- # segment_files <- segment_files %>% filter(!grepl("aoi3_*.*merge.geojson", file)) -->
<!-- #  -->
<!-- # # area and quiet func -->
<!-- # ha <- function(x) as.numeric(units::set_units(st_area(x), "ha")) -->
<!-- # quiet <- function(x) suppressWarnings(suppressMessages(x)) -->

<!-- humachine_sum <- tile_aoi_validation_stats$aoi %>%  -->
<!--   select(type, aoi, area_mu, area_med) %>%  -->
<!--   rename(Mean = area_mu, Median = area_med) %>%  -->
<!--   tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat") %>%  -->
<!--   tidyr::pivot_wider(names_from = type, values_from = value) -->

<!-- aoi_wide <- tile_aoi_validation_stats$aoi %>% group_by(type) %>%  -->
<!--   summarize(Mean = weighted.mean(area_mu, w = n),  -->
<!--             Median = weighted.mean(area_med, w = n)) %>%  -->
<!--   tidyr::pivot_longer(cols = Median:Mean, names_to = "Stat") %>%  -->
<!--   tidyr::pivot_wider(names_from = type, values_from = value) %>%  -->
<!--   mutate(aoi = "All") %>% select(aoi, !!names(.)) -->

<!-- p <- ggplot(humachine_sum) + -->
<!--   geom_point(aes(x = segments, y = validation)) +  -->
<!--   geom_point(data = aoi_wide, aes(x = segments, y = validation), color = "red") +  -->
<!--   scale_x_continuous(limits = c(0, 8)) +  -->
<!--   scale_y_continuous(limits = c(0, 8)) +  -->
<!--   ggrepel::geom_text_repel( -->
<!--     aes(label = aoi, x = segments, y = validation), col = "grey50",  -->
<!--     segment.color = "grey60", point.padding = 0.1, min.segment.length = 0.2, -->
<!--     segment.size = 0.2, size = 3    -->
<!--   ) +  -->
<!--   xlab("Segmentation field size (ha)") + ylab("Validation field size (ha)") +  -->
<!--   geom_abline(slope = 1) + facet_wrap(vars(Stat)) +  -->
<!--   theme_linedraw() +  -->
<!--   theme(strip.background = element_rect(fill = "white"),  -->
<!--         strip.text = element_text(colour = "black")) -->

<!-- ``` -->

>>>>

### Figure S3: PlanetScope image density
The density of imagery available for download from the image catalog.

```{r imagedensity, eval=FALSE}
img_density <- st_read(
  system.file("extdata/img_catalog_count_201712_201902.geojson", 
              package = "activemapper")
)

tile_count <- img_density %>% mutate(season = case_when(
  year == 2018 & month %in% 5:9 ~ "GS",
  year == 2018 & month %in% 12 ~ "OS", 
  year == 2019 & month %in% 1:2 ~ "OS", 
  TRUE ~ NA_character_)
) %>% filter(season %in% c("GS", "OS")) %>% 
  as_tibble() %>%
  group_by(tile, season) %>%
  summarize(Count = sum(count))

gs_count <- tiles %>% dplyr::select(tile) %>% 
  left_join(., tile_count %>% filter(season == "GS"))
os_count <- tiles %>% dplyr::select(tile) %>% 
  left_join(., tile_count %>% filter(season == "OS")) # %>%
  # fasterize::fasterize(., field = "count")

pal <- colorRampPalette(rev(RColorBrewer::brewer.pal(9, "RdBu")))
zlim <- range(c(gs_count$Count, os_count$Count))
p <- ggplot() + 
  geom_sf(data = gs_count, aes(fill = Count), col = "transparent") + 
  geom_sf(data = aois, fill = "transparent", size = 0.2) + 
  scale_fill_gradientn(colours = pal(20), limits = zlim) +
  ggtitle("May - Sept 2018") + 
  theme_void() + 
  theme(legend.position = "none", 
        title = element_text(size = 9))

p2 <- ggplot() + 
  geom_sf(data = os_count, aes(fill = Count), col = "transparent") + 
  scale_fill_gradientn(colours = pal(20), limits = zlim) +
  geom_sf(data = aois, fill = "transparent", size = 0.2) + 
  ggtitle("Dec 2018 - Feb 2019") +
  theme_void() + 
  theme(title = element_text(size = 9),
        legend.text = element_text(size = 9))

op <- p + p2
ggsave(op, bg = "transparent",
       filename = pth("figures/si_planet_coverage.png"), 
       width = 5, height = 3, dpi = 300, units = "in")

### Figure S4: Initial training site distribution
Figure showing distribution of initial 500 samples per cluster, as well as distribution of points per iteration.  
```{r trainingsites, eval=FALSE}
data("train_val_sites")

@@

### Figure S5: Label count and quality
```{r labelquality, eval=FALSE}
data("label_summary")

@@

### Figures S6 and S7: Consensus label (Bayesian) risk

@@

### Figure S8: Random versus active sampling
```{r, eval=FALSE}
data("iteration_metrics")

@@

### Figure S9: Training data error impact on probability images
```{r, eval = FALSE}
probpal <- viridis::viridis
cprob <- raster(here::here("external/prob/image_c294_r532.tif"))
hprob <- raster(here::here("external/prob/image_c294_r532_high.tif"))
lprob <- raster(here::here("external/prob/image_c294_r532_low.tif"))

@@

### Figure S10: AOI Zones

@@

### Figures S11 and S12: Segmentation statistics (grid scale)

@@

### Figure S13: Average fields sizes

@@
